%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% History
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{History of Artificial Life}

%% 2. History of AI and Computing, Turing, VonNue, etc
%%    History with ALife, Langton, GameOfLife
%%
%%      Charles Darwin
%% 1937 Alan Turing
%% 1945 John von Neumann
%%      Wolfram
%% 1970 Cellular automaton, John Conway
%% 1986 Christopher Langton
%%      Marvin Minsky

History of artificial life.  artificial intelligence, cellular automata, sixty
years ago.

Charles Darwin, Alan Turning, John von Neumann, Wolfram, John McCarthy

If we really wanted to create a thorough simulation of life, we should model
everything in our Universe.  We should go back to the big bang.  We should go
back to early earth and model the earth formations.  We should look at the first
forms of cell life.  Model water and geodesic reactions.  We should look at
everything several billion years ago and then model as much as we can from that
point and model several billion years later.

Just the thought of several billion years ago and modeling chemical reactions
and water, sun, early life.  If our goal is to model 4 billion years of earth's
history with the goal of researching complex life forms.  Just consider the
complex life on earth today.  There are 6 billion humans alive today post 4
billion years since the earth's creation.  We estimate  that 100 billion humans
have lived.

That assumes that you only consider human life to be interesting.  What about
all the other forms of interesting life forms that have lived.  How many insect
have lived since early earth.  The numbers are infestimal.

Accurately modeling ... the Universe is complex.   Modeling the earth is equally
complex.

So, we have to focus on the more interesting aspects of early life and biology.

Let's look at organic material vs inorganic

DNA, Life, Death, Mutations, Evolution.  Blind Watchmaker